Circular Regression Trees and Forests with an Application to Probabilistic Wind Direction Forecasting

### 2019-12-04 pkg/circtree/inst/wind_paper/draft/draft.Rnw
Inlcude circular splits
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2912 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: d790f4ba845d72736312c0db11d98237da9fd2e2

% TODO: circular splits (see first version of IWSM, 4 pages)

>>>>

Another possible improvement for obtaining more parsimonious circular trees is
to consider splitting circular covariates into two circle segments by searching
two split points simultaneously rather than sequentially at different depths.
While this might slightly improve the predictive performance of circular trees,
this should not affect the performance  of circular forest, as these still typically 
consist of very large trees with many different splits.
